Contribution Title\thanks{Supported by organization x.}

### 2019-05-06 main.tex
Fix

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We develop yet another typed multi-stage calculus Lambda-MD. It extends Hanada and Igarashi's Lambda-TP with dependent type.

@@

In this article, we design Lambda-MD by introducing dependent type into Lamda-TP. It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization. In addition, we define an evaluation context which takes stages into account. Under the evaluation context progress is hold.

@@

199 words

>>>>

\begin{document}
%
\title{Contribution Title\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Akira Kawata\inst{1} \and
Atsushi Igarashi\inst{2}\orcidID{0000-0002-5143-9764}}
%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Graduate School of Informatics, Kyoto University, Kyoto, Japan\\
\email{akira@kuis.kyoto-u.ac.jp} \and
\email{igarashi@kuis.kyoto-u.ac.jp}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
We develop yet another typed multi-stage calculus $\lambda^{\textrm{MD}}$.
It extends Hanada and Igarashi's $\lambda^{\triangleright\%}$ with dependent type.

@@

In this article, we design $\lambda^{\textrm{MD}}$ by introducing dependent type into Lamda-TP.
It has a simple, substitution-based full-reduction semantics and enjoys basic properties of subject reduction, confluence, and strong normalization.
In addition, we define an evaluation context which takes stages into account. Under the evaluation context progress is hold.

@@

Finally, we discuss the relationship between Cross Stage Persistent and decidability of type checking.
If you import dependent type to multi-stage calculus naively, the type checking may fail into an infinite loop and doesn't finish forever.
We impose a little restriction on typing rules and made the type checking finish in finite time.

238 words
